# Visualization

In this chapter I created home range maps by tamarin group

```{r, message = FALSE}
library(sf)
library(sp)
library(dplyr)
library(adehabitatHR)
library(tidyverse)
```

First, I converted my "groups" data frame to a spatial points data frame and projected to 
UTM
```{r}
groups <- readRDS("groups.RDS")

groups_a <- groups %>%
  dplyr::select(group_id, lon, lat)

coordinates(groups_a) <- c("lon", "lat")

proj4string(groups_a) <- CRS("+init=epsg:4326") # define crs

groups_a <- sp::spTransform(groups_a, CRS = CRS("+init=epsg:32738")) # project to UTM
```

Next, I calculated and plotted home ranges by group using kernel density estimation 
```{r, message = FALSE, warning = FALSE}
library(scales) # allows me to make polygons partly transparent using alpha argument

ud <- kernelUD(groups_a, h = "href")

hr <- getverticeshr(ud, percent = 95) # hr is in hectares 

as_tibble(hr) # shows home range in hectares of each group 

plot(hr, col = alpha(1:3, 0.5))

legend("topright", legend = hr$id, lty = 1, col = alpha(1:3),
       title = "Group ID")

```

Here I plotted both spatial points and polygons together by group
```{r}
library(graphics)

plot(groups_a, col = as.factor(groups_a@data$group_id), pch = 16)

plot(hr, col = alpha(1:3, 0.5), add = TRUE)

legend("topright", legend = hr$id, lty = 1, col = alpha(1:3),
       title = "Group ID")

```

This is similar to the plot above, however I used the sf and ggplot2 packages
instead. 
```{r}
library(sf)

groups_sf <- st_as_sf(groups_a)

groups_hr <- st_as_sf(hr)

ggplot() + 
  geom_sf(data = groups_sf, aes(fill = group_id)) + 
  geom_sf(data = groups_hr, aes(fill = id)) + 
  scale_fill_manual(values = alpha(1:3, 0.3)) + 
  theme_bw()

```

